data_collation

### 2024-04-12 scripts/data_collation.Rmd
commbined data frames by category, some questions for cleaning up dataa for austin
cleaning up data

# COVER data frame is its own category, is this supposed to combine with another? it was labeled, Kelp_COVER

@@

@@

@@

@@

@@

@@

#delete repetative data collector columns
kelp_data <- kelp_data[ -c(13:16) ]

>>>>

#delete repetative data collector columns
kelp_data <- kelp_data[ -c(11:17) ]

@@

# remove columns with observer and unneeded data
fish_data <- fish_data[ -c(10:13) ]

# fish dataframe has size in wide format, discuss I can change this to long is you want but wanted to make sure size classes matched

@@

# Rename ft. wetherill to fort wetherill
UPC_data$SITE[UPC_data$SITE == "Ft. Weatherill"] <- "Fort Wetherill"

# remove columns with observer and unneeded data
UPC_data <- UPC_data[ -c(21:24) ]
```

@@

# Rename ft. wetherill to fort wetherill
swath_data$SITE[swath_data$SITE == "Ft.Weatherill"] <- "Fort Wetherill"

@@

# remove columns with observer and unneeded data
morph_data <- morph_data[ -c(11:14) ]
```

@@

# Rename ft. wetherill to fort wetherill
QUAD_data$SITE[QUAD_data$SITE == "Ft Wetherill"] <- "Fort Wetherill"

@@
